Visualization of Fractional Integrals

### 2019-03-13 fractional/CMJ style files/article-template.tex
improved section on gamma function

\section{Gamma Function}
The gamma function is defined for all real numbers except for the non-negative integers. Moreover, it is a natural extends the factorial of an integer 
to any real number. The Gamma function is defined as:
\begin{equation}
\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt
\end{equation}

>>>>

\section{Gamma Function}
The gamma function was first devised by Euler. The gamma function is defined for all real numbers except for the non-negative integers. Moreover, it is a natural extension of the factorial function to the real numbers. The Gamma function is defined as:
\begin{equation}
\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt
\end{equation}
\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{gamma.pdf}
\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
\label{fig:gamma}
\end{figure}
